Paper Analysis

### 2025-05-05 Paper_WriteUp/Paper_Plots.qmd
fixing breaks and limits for various plot axes

comp_global = bind_rows(pars_17_19, pars_20_22, pars_23_25, pars_gm) |> 
  ggplot(aes(x = value, y = name, color = factor(model, levels = c("1700-1900", "2000-2200", "2300-2500", "GM")))) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  facetted_pos_scales(x = list( #for customizing scales on each facet
    name == "mu_beta" ~ scale_x_continuous(breaks = c(-0.15, 0, 0.15), limits = c(-0.17, 0.17)),
    name == "gamma1" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma2" ~ scale_x_continuous(breaks = breaks_pretty(n = 2))
  )) +
  scale_color_viridis_d(option = "H")

@@

#plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.125, 0.125)) +
  theme_single_y()

@@

## count how many intervals contain 0
## see how many contain 0
player_pars |> 
  group_by(player_name, param) |> 
  filter(param == 2) |> 
  summarise(lower = quantile(value, prob = 0.025),
            upper = quantile(value, prob = 0.975)) |> 
  mutate(contain_zero = ifelse(upper > 0 & lower < 0,
                         1, 0)) |> 
  filter(contain_zero == 0)

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |>
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.125, 0.125)) +
  theme_single_y()

@@

#plot
bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |>
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  facet_wrap(~name,
    scales = "free",
    labeller = labeller(name = facet_labels)
  ) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  facetted_pos_scales(x = list( #for customizing scales on each facet
    name == "mu_beta" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma1" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma2" ~ scale_x_continuous(breaks = breaks_pretty(n = 2))
  )) +
  #scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

>>>>

comp_global = bind_rows(pars_17_19, pars_20_22, pars_23_25, pars_gm) |> 
  ggplot(aes(x = value, y = name, color = factor(model, levels = c("1700-1900", "2000-2200", "2300-2500", "GM")))) +
  stat_pointinterval(position = position_dodge(width = 0.3)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  facetted_pos_scales(x = list( #for customizing scales on each facet
    name == "mu_beta" ~ scale_x_continuous(breaks = c(-0.05, 0, 0.05), limits = c(-0.07, 0.07)),
    name == "gamma1" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma2" ~ scale_x_continuous(breaks = breaks_pretty(n = 2))
  )) +
  scale_color_viridis_d(option = "H")

@@

#plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.075, 0.075)) +
  theme_single_y()

@@

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |>
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.075, 0.075)) +
  theme_single_y()

@@

#plot
bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |>
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  facet_wrap(~name,
    scales = "free",
    labeller = labeller(name = facet_labels)
  ) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  facetted_pos_scales(x = list( #for customizing scales on each facet
    name == "gamma1" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma2" ~ scale_x_continuous(breaks = c(0.0052, 0.0056), limits = c(0.0051, 0.0058)),
    name == "mu_beta" ~ scale_x_continuous(breaks = c(-0.1, 0, 0.1))
  )) +
  #scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")
